Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2020-11-02 bbbq_article.tex
Tables fit on paper
Show 8k random sequences

Evolutionary conservation scores are shown in 
figures \ref{fig:evolutionary_conservation} (topology),
\ref{fig:evolutionary_conservation_violin} (per 
protein with at least 1 TMH, violin)
and \ref{fig:evolutionary_conservation_merged} (grouped 
from all proteins that have at least 1 TMH).
See figures
\ref{fig:evolutionary_conservation_all} and 
\ref{fig:evolutionary_conservation_all_violin}
for the scores for all proteins).

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_2/scores.png}
  \caption{
    Conservation scores for the aligned SARS-CoV-2 proteomes,
    for proteins that have at least one TMH.
    The (non-logarithmic) scale of the conservation score has been removed
    for readability.
    Conservation scores do not start at residue 1 when
    an aligned protein sequence outflanks the consensus sequence 
    at the N-terminal
  }
  \label{fig:evolutionary_conservation}
\end{figure}

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_2/scores_merged_violin.png}
  \caption{
    Evolutionary conservation scores of TMH versus non-TMH
    residues in the SARS-CoV-2 proteome,
    with conservation scores group from all proteins that have at least one TMH
  }
  \label{fig:evolutionary_conservation_merged}
\end{figure}

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_2/scores_violin.png}
  \caption{
    Evolutionary conservation scores of TMH versus non-TMH
    residues in the SARS-CoV-2 proteome,
    for proteins that have at least one TMH
  }
  \label{fig:evolutionary_conservation_violin}
\end{figure}

@@

% Percentage of MHC-I 9-mers overlapping with TMH. Values in brackets
% show the number of binders that have at least one residue overlapping with a
% TMH (first value)as well as the number of binders (second value). Percentile
% used: 0.02
% Label: tab:tmh_binders_mhc1
\input{bbbq_1_fast/table_tmh_binders_mhc1.latex}

@@

\input{bbbq_1_fast/table_tmh_binders_mhc2.latex}

@@

\begin{figure}[!htbp]
  \includegraphics[width=0.7\textwidth,scale=0.7]{bbbq_2/scores_all.png}
  \caption{
    Conservation scores for the aligned SARS-CoV-2 proteomes,
    for all proteins.
    The (non-logarithmic) scale of the conservation score has been removed
    for readability.
    Conservation scores do not start at residue 1 when
    an aligned protein sequence outflanks the consensus sequence 
    at the N-terminal.
  }
  \label{fig:evolutionary_conservation_all}
\end{figure}

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_2/scores_violin_all.png}
  \caption{
    Evolutionary conservation scores of TMH versus non-TMH
    residues in the SARS-CoV-2 proteome,
    for all proteins
  }
  \label{fig:evolutionary_conservation_all_violin}
\end{figure}

>>>>

Evolutionary conservation scores are shown in 
figures \ref{fig:evolutionary_conservation_8k} (topology),
\ref{fig:evolutionary_conservation_8k_violin} (per 
protein with at least 1 TMH, violin)
and \ref{fig:evolutionary_conservation_8k_merged} (grouped 
from all proteins that have at least 1 TMH).
See figures
\ref{fig:evolutionary_conservation_8k_all} and 
\ref{fig:evolutionary_conservation_8k_all_violin}
for the scores for all proteins).

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_2/8000_42/scores.png}
  \caption{
    Conservation scores for the aligned SARS-CoV-2 proteomes,
    for proteins that have at least one TMH,
    from a subset of 8000 randomly selected SARS-CoV-2 sequences.
    The (non-logarithmic) scale of the conservation score has been removed
    for readability.
    Conservation scores do not start at residue 1 when
    an aligned protein sequence outflanks the consensus sequence 
    at the N-terminal
  }
  \label{fig:evolutionary_conservation_8k}
\end{figure}

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_2/8000_42/scores_merged_violin.png}
  \caption{
    Evolutionary conservation scores of TMH versus non-TMH
    residues in the SARS-CoV-2 proteome,
    with conservation scores group from all proteins that have at least one TMH,
    from a subset of 8000 randomly selected SARS-CoV-2 sequences.
  }
  \label{fig:evolutionary_conservation_8k_merged}
\end{figure}

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_2/8000_42/scores_violin.png}
  \caption{
    Evolutionary conservation scores of TMH versus non-TMH
    residues in the SARS-CoV-2 proteome,
    for proteins that have at least one TMH,
    from a subset of 8000 randomly selected SARS-CoV-2 sequences.
  }
  \label{fig:evolutionary_conservation_8k_violin}
\end{figure}

@@

% Percentage of MHC-I 9-mers overlapping with TMH. Values in brackets
% show the number of binders that have at least one residue overlapping with a
% TMH (first value)as well as the number of binders (second value). Percentile
% used: 0.02
% Label: tab:tmh_binders_mhc1
%\begin{sidewaystable}
%  \centering
%  ... centered table here
%\end{sidewaystable}

% \scalebox{0.7}{
%  ... scaled table here
% }

%{\tiny
%  ... something with a tiny font
%}

\input{bbbq_1_fast/table_tmh_binders_mhc1.latex}

@@

%\begin{sidewaystable}
%  \centering
  \input{bbbq_1_fast/table_tmh_binders_mhc2.latex}
%\end{sidewaystable}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Subset of random sequences}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_2/8000_42/scores.png}
  \caption{
    Conservation scores for the aligned SARS-CoV-2 proteomes,
    for proteins that have at least one TMH,
    from a subset of 8000 randomly selected SARS-CoV-2 sequences.
    The (non-logarithmic) scale of the conservation score has been removed
    for readability.
    Conservation scores do not start at residue 1 when
    an aligned protein sequence outflanks the consensus sequence 
    at the N-terminal
  }
  \label{fig:evolutionary_conservation_8k}
\end{figure}

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_2/8000_42/scores_merged_violin.png}
  \caption{
    Evolutionary conservation scores of TMH versus non-TMH
    residues in the SARS-CoV-2 proteome,
    with conservation scores group from all proteins that have at least one TMH,
    from a subset of 8000 randomly selected SARS-CoV-2 sequences.
  }
  \label{fig:evolutionary_conservation_8k_merged}
\end{figure}

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_2/8000_42/scores_violin.png}
  \caption{
    Evolutionary conservation scores of TMH versus non-TMH
    residues in the SARS-CoV-2 proteome,
    for proteins that have at least one TMH,
    from a subset of 8000 randomly selected SARS-CoV-2 sequences.
  }
  \label{fig:evolutionary_conservation_8k_violin}
\end{figure}

\begin{figure}[!htbp]
  \includegraphics[width=0.7\textwidth,scale=0.7]{bbbq_2/8000_42/scores_all.png}
  \caption{
    Conservation scores for the aligned SARS-CoV-2 proteomes,
    for all proteins,
    from a subset of 8000 randomly selected SARS-CoV-2 sequences.
    The (non-logarithmic) scale of the conservation score has been removed
    for readability.
    Conservation scores do not start at residue 1 when
    an aligned protein sequence outflanks the consensus sequence 
    at the N-terminal.
  }
  \label{fig:evolutionary_conservation_8k_all}
\end{figure}

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_2/8000_42/scores_violin_all.png}
  \caption{
    Evolutionary conservation scores of TMH versus non-TMH
    residues in the SARS-CoV-2 proteome,
    for all proteins,
    from a subset of 8000 randomly selected SARS-CoV-2 sequences.
  }
  \label{fig:evolutionary_conservation_8k_all_violin}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{All unique sequences}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_2/scores.png}
  \caption{
    Conservation scores for the aligned SARS-CoV-2 proteomes,
    for proteins that have at least one TMH,
    using all unique sequences \richel{which I doubt is valid}.
    The (non-logarithmic) scale of the conservation score has been removed
    for readability.
    Conservation scores do not start at residue 1 when
    an aligned protein sequence outflanks the consensus sequence 
    at the N-terminal
  }
  \label{fig:evolutionary_conservation_all_unique}
\end{figure}

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_2/scores_merged_violin.png}
  \caption{
    Evolutionary conservation scores of TMH versus non-TMH
    residues in the SARS-CoV-2 proteome,
    with conservation scores group from all proteins that have at least one TMH,
    using all unique sequences \richel{which I doubt is valid}.
  }
  \label{fig:evolutionary_conservation_all_unique_merged}
\end{figure}

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_2/scores_violin.png}
  \caption{
    Evolutionary conservation scores of TMH versus non-TMH
    residues in the SARS-CoV-2 proteome,
    for proteins that have at least one TMH,
    using all unique sequences \richel{which I doubt is valid}.
  }
  \label{fig:evolutionary_conservation_all_unique_violin}
\end{figure}

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_2/scores.png}
  \caption{
    Conservation scores for the aligned SARS-CoV-2 proteomes,
    for proteins that have at least one TMH,
    using all unique sequences \richel{which I doubt is valid}.
    The (non-logarithmic) scale of the conservation score has been removed
    for readability.
    Conservation scores do not start at residue 1 when
    an aligned protein sequence outflanks the consensus sequence 
    at the N-terminal
  }
  \label{fig:evolutionary_conservation_all_unique}
\end{figure}

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_2/scores_merged_violin.png}
  \caption{
    Evolutionary conservation scores of TMH versus non-TMH
    residues in the SARS-CoV-2 proteome,
    with conservation scores group from all proteins that have at least one TMH,
    using all unique sequences \richel{which I doubt is valid}.
  }
  \label{fig:evolutionary_conservation_all_unique_merged}
\end{figure}

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_2/scores_violin.png}
  \caption{
    Evolutionary conservation scores of TMH versus non-TMH
    residues in the SARS-CoV-2 proteome,
    for proteins that have at least one TMH,
    using all unique sequences \richel{which I doubt is valid}.
  }
  \label{fig:evolutionary_conservation_all_unique_violin}
\end{figure}

\begin{figure}[!htbp]
  \includegraphics[width=0.7\textwidth,scale=0.7]{bbbq_2/scores_all.png}
  \caption{
    Conservation scores for the aligned SARS-CoV-2 proteomes,
    for all proteins,
    using all unique sequences \richel{which I doubt is valid}.
    The (non-logarithmic) scale of the conservation score has been removed
    for readability.
    Conservation scores do not start at residue 1 when
    an aligned protein sequence outflanks the consensus sequence 
    at the N-terminal.
  }
  \label{fig:evolutionary_conservation_all_unique_all}
\end{figure}

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_2/scores_violin_all.png}
  \caption{
    Evolutionary conservation scores of TMH versus non-TMH
    residues in the SARS-CoV-2 proteome,
    for all proteins,
    using all unique sequences \richel{which I doubt is valid}.
  }
  \label{fig:evolutionary_conservation_all_unique_all_violin}
\end{figure}
